Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2020-09-18 manuscript/climate_sensitivity_SI.Rmd
Added citation names for R packages

[@R-base; @R-broom; @R-car; @R-cowplot; @R-data.table; @R-devtools; @R-dplR; @R-dplyr; @R-extrafont; @R-ggplot2; @R-ggpubr; @R-ggthemes; @R-gridExtra; @R-knitr; @R-lubridate; @R-MuMIn; @R-piecewiseSEM; @R-png; @R-purrr; @R-raster; @R-rasterVis; @R-RCurl; @R-readxl; @R-reshape2; @R-rgdal; @R-rgeos; @R-rmarkdown; @R-sf; @R-stringi; @R-stringr; @R-tidyr]

>>>>

R base [@R-base]; broom [@R-broom]; car [@R-car]; cowplot [@R-cowplot]; data.table [@R-data.table]; devtools [@R-devtools]; dplR [@R-dplR]; dplyr [@R-dplyr]; extrafont [@R-extrafont]; ggplot2 [@R-ggplot2]; ggpubr [@R-ggpubr]; ggthemes [@R-ggthemes]; gridExtra [@R-gridExtra]; knitr [@R-knitr]; lubridate [@R-lubridate]; MuMIn [@R-MuMIn]; piecewiseSEM [@R-piecewiseSEM]; png [@R-png]; purrr [@R-purrr]; raster [@R-raster]; rasterVis [@R-rasterVis]; RCurl [@R-RCurl]; readxl [@R-readxl]; reshape2 [@R-reshape2]; rgdal [@R-rgdal]; rgeos [@R-rgeos]; rmarkdown [@R-rmarkdown]; sf [@R-sf]; stringi [@R-stringi]; stringr [@R-stringr]; tidyr [@R-tidyr]
